Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-19 paper/paper.tex
Convert to IEEE format

\documentclass{sig-alternate}
\usepackage{algorithm,algpseudocode}
\usepackage{url}

@@

\conferenceinfo{HPDC}{'12 Delft, The Netherlands}
% \CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden
% - IF NEED BE. \crdata{0-12345-67-8/90/01}  % Allows default copyright data
% (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.

\title{Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}
% \subtitle{[Extended Abstract]}

\numberofauthors{3}
\author{
    \alignauthor Maciej Malawski\\
       \affaddr{AGH University of Science and Technology}\\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{Krakow, Poland; and}\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 ITC, Notre Dame, IN, USA}\\
       \email{mmalawsk@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
    \alignauthor Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 ITC, Notre Dame, IN, USA}\\
       \email{naber@nd.edu}
}

@@

\category{H.3.4}{Systems and Software}{Distributed systems}
\category{D.4.8}{Performance}{Simulation}

\terms{DAG, Scheduling, Simulation}

\keywords{Scientific workflows, Workflow ensembles,
Cloud computing, Infrastructure-as-a-Service}

@@

%\section{Acknowledgments}
%Acknowledgements go here.

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\documentclass[conference]{IEEEtran}

\usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
\graphicspath{{./figures/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm,algpseudocode}
\usepackage{url}

@@

% can use linebreaks \\ within to get better formatting as desired
\title{Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
  \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

% ACM Format
%\numberofauthors{3}
%\author{
%    \alignauthor Maciej Malawski\\
%       \affaddr{AGH University of Science and Technology}\\
%       \affaddr{Dept. of Computer Science}\\
%       \affaddr{Krakow, Poland; and}\\
%       \affaddr{University of Notre Dame}\\
%       \affaddr{Center for Research Computing}\\
%       \affaddr{111 ITC, Notre Dame, IN, USA}\\
%       \email{mmalawsk@nd.edu}
%    \alignauthor Gideon Juve and Ewa Deelman\\
%       \affaddr{USC Information Sciences Institute}\\
%       \affaddr{4676 Admiralty Way}\\
%       \affaddr{Marina del Rey, CA, USA}\\
%       \email{\{gideon,deelman\}@isi.edu}
%    \alignauthor Jarek Nabrzyski\\
%       \affaddr{University of Notre Dame}\\
%       \affaddr{Center for Research Computing}\\
%       \affaddr{111 ITC, Notre Dame, IN, USA}\\
%       \email{naber@nd.edu}
%}

@@

% IEEE does not have these
%\category{H.3.4}{Systems and Software}{Distributed systems}
%\category{D.4.8}{Performance}{Simulation}
%\terms{DAG, Scheduling, Simulation}
%\keywords{Scientific workflows, Workflow ensembles, Cloud computing, Infrastructure-as-a-Service}

@@

%\section*{Acknowledgments}
%Acknowledgements go here.

% ACM style
%\bibliographystyle{abbrv}
% IEEE style
\bibliographystyle{IEEEtran}

\bibliography{paper}
